---
title: "Time-Series Plots"
author: "June"
date: '2020 3 30 '
output: html_document
---
(@) ***SESS_ID_SUM***

+ SESS_ID_SUM Data Setting

```{r code1, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

test <- M_ALL_2[!duplicated(M_ALL_2[,c("SESS_ID","SESS_DT")]),]
test <- test[,c("SESS_ID","SESS_DT")]
test$SESS_DT <- as.Date(test$SESS_DT)

test <- test %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(SESS_ID_SUM = n())

```

+ SESS_ID_SUM Visualization

```{r code2, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

greem8 <- ggplot( test, aes(x = SESS_DT, y = SESS_ID_SUM)) + 
  geom_line(size = 1, color = 'Black') +
  ggtitle("M_ALL_2 SESS_ID_SUM 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  # geom_hline(yintercept=mean(test), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem8

```


(@) ***HITS_SEQ_SUM***

+ HITS_SEQ_SUM Data Setting

```{r code3, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

M_ALL_3 <- M_ALL_2 %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(HITS_SEQ_SUM = sum(HITS_SEQ))

```

+ HITS_SEQ_SUM Visualization

```{r code4, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

M_ALL_3$SESS_DT <- as.Date(M_ALL_3$SESS_DT)

greem1 <- ggplot( M_ALL_3, aes(x = SESS_DT, y = HITS_SEQ_SUM)) + 
  geom_line(size = 1, color = '#800000') +
  ggtitle("M_ALL_2 HITS_SEQ_SUM 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  geom_hline(yintercept=mean(M_ALL_3$HITS_SEQ_SUM), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem1

```


(@) ***PD_C_SUM***

+ PD_C_SUM Data Setting

```{r code5, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

testp <- M_ALL_2[,c("PD_C","SESS_DT")]

test_p <- testp %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(PD_C_SUM = n())

test_p$SESS_DT <- as.Date(test_p$SESS_DT)
```

+ PD_C_SUM Visualization

```{r code6, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

greem7 <- ggplot( test_p, aes(x = SESS_DT, y = PD_C_SUM)) + 
  geom_line(size = 1, color = 'Blue') +
  ggtitle("M_ALL_2 PD_C_SUM 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  # geom_hline(yintercept=mean(test), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem7

```


(@) ***PD_BUY_AM_MEAN***

+ PD_BUY_AM_MEAN Data Setting

```{r code7, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

M_ALL_3 <- M_ALL_2 %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(PD_BUY_AM_MEAN = mean(PD_BUY_AM))

M_ALL_3$SESS_DT <- as.Date(M_ALL_3$SESS_DT)

```

+ PD_BUY_AM_MEAN Visualization

```{r code8, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

greem2 <- ggplot( M_ALL_3, aes(x = SESS_DT, y = PD_BUY_AM_MEAN)) + 
  geom_line(size = 1, color = '#228B22') +
  ggtitle("M_ALL_2 PD_BUY_AM_MEAN 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  geom_hline(yintercept=mean(M_ALL_3$PD_BUY_AM_MEAN), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem2
```


(@) ***PD_BUY_CT_SUM***

+ PD_BUY_AM_MEAN Data Setting

```{r code9, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

M_ALL_3 <- M_ALL_2 %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(PD_BUY_CT_SUM = sum(PD_BUY_CT))

M_ALL_3$SESS_DT <- as.Date(M_ALL_3$SESS_DT)

```

+ PD_BUY_AM_MEAN Visualization

```{r code10, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

greem3 <- ggplot( M_ALL_3, aes(x = SESS_DT, y = PD_BUY_CT_SUM)) + 
  geom_line(size = 1, color = '#F08080') +
  ggtitle("M_ALL_2 PD_BUY_CT_SUM 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  geom_hline(yintercept=mean(M_ALL_3$PD_BUY_CT_SUM), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem3
```


(@) ***TOTPAG_VIEW_CT_SUM***

+ TOTPAG_VIEW_CT_SUM Data Setting

```{r code11, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

M_ALL_3 <- M_ALL_2 %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(TOT_PAG_VIEW_CT_SUM = sum(TOT_PAG_VIEW_CT))

M_ALL_3$SESS_DT <- as.Date(M_ALL_3$SESS_DT)

```

+ TOT_PAG_VIEW_CT_SUM Visualization

```{r code12, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

greem4 <- ggplot( M_ALL_3, aes(x = SESS_DT, y = TOT_PAG_VIEW_CT_SUM)) + 
  geom_line(size = 1, color = '#48D1CC') +
  ggtitle("M_ALL_2 TOT_PAG_VIEW_CT_SUM 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  geom_hline(yintercept=mean(M_ALL_3$TOT_PAG_VIEW_CT_SUM), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem4
```


(@) ***TOT_SESS_HR_V_SUM***

+ TOT_SESS_HR_V_SUM Data Setting

```{r code13, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

M_ALL_3 <- M_ALL_2 %>% 
  arrange(SESS_DT) %>% 
  group_by(SESS_DT) %>% 
  summarise(TOT_SESS_HR_V_SUM = sum(TOT_SESS_HR_V))

M_ALL_3$SESS_DT <- as.Date(M_ALL_3$SESS_DT)

```

+ TOT_SESS_HR_V_SUM Visualization

```{r code14, eval=FALSE, include=TRUE, echo=TRUE, message=FALSE, warning=FALSE}

greem5 <- ggplot( M_ALL_3, aes(x = SESS_DT, y = TOT_SESS_HR_V_SUM)) + 
  geom_line(size = 1, color = '#7B68EE') +
  ggtitle("M_ALL_2 TOT_SESS_HR_V_SUM 시계열 Plot") +
  theme_bw() +
  labs(x="", y="") +
  scale_x_date( date_breaks = "1 month", 
                date_labels = '%m/%d') +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  geom_hline(yintercept=mean(M_ALL_3$TOT_SESS_HR_V_SUM), linetype='dashed') +
  theme(plot.title = element_text( hjust = 0.5, 
                                   size = 18, color = "darkblue"))
greem5
```
